---
title: "BUAN_5310 Group_Project"
author: "Florence Yan, Haodi Tu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '3'
  html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r message = FALSE, echo = FALSE, error = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


# 1. Data Loading and Preperation
```{r message = FALSE, echo = FALSE, error = FALSE}
library(tidyverse)
library(GGally)
library(janitor)
library(kableExtra)
library(htmlTable)
library(ggplot2)
library(readxl)
library(gridExtra)
```


```{r}
# Load data
# acs <- read.csv('airport_choice_survey.csv')
# traffic <- read.csv('traffic.csv')
# province <- read.csv('province.csv')
# price <- read.csv('price.csv')

acs <- read_excel("airport_choice_survey_EN_ver2.0_Capstone.xlsx", sheet = 'Data')
traffic <- read_excel("Airport_Airline_data.xlsx", sheet = 1)
province <- read_excel("Airport_Airline_data.xlsx", sheet = 3)
price <- read_excel("Airport_Airline_data.xlsx", sheet = 2)
```


```{r}
# Rename columns in R
names(acs)[1]<-"ID"
names(price)[1] <- "Airport"
names(province)[1] <- "Airport"
names(province)[4] <- "Travel.time.min"
names(traffic)[1] <- "Airport"
```


```{r}
str(acs)
# summary(acs)
```

+ Data type transfermation:
    + Numeric to chr: Gender, Nationality, ProvinceResidence, GroupTravel, Destination, DepartureTime, SeatClass, ModeTransport, Occupation, Income
    
+ Missing values 
    + Eliminate missing values from Airline, age, gender, destination, ?(Airfare, AccessCost, AccessTime)

+ Remove unwanted variables
    + FlightNo: Don't match any other variables from data;
    + DepartureHr: is same as DepartureTime, just more specific;
    + DepartureMn: values are from 0-60 min. Don't think it will affect result much and too many missing values
    + MileageAirline: unknown letters
    + Mileage: too many missing values, three fourth of total observations
    



```{r}
# Data cleaning
acs[2] <- ifelse(acs[2] == 1, 'ICN', 'GMP') 
  
acs[3] <- ifelse(acs[3] == 1, 'Korean',
           (ifelse(acs[3] == 2, 'Korean',
              (ifelse(acs[3] == 3, 'Korean', 'Foreign'))))
                   )
acs[4] <- ifelse(acs[4] <= 50 , '<=50', '>50')
acs[7] <- ifelse(acs[7] == 1, 'Leisure', 'Business')
```



```{r}
# Convert data type 
acs$Gender <- as.character(acs$Gender)
acs$Nationality <-as.character(acs$Nationality)
acs$ProvinceResidence <-as.character(acs$ProvinceResidence)
acs$GroupTravel <-as.character(acs$GroupTravel)
acs$Destination <-as.character(acs$Destination)
acs$DepartureTime <-as.character(acs$DepartureTime)
acs$SeatClass <-as.character(acs$SeatClass)
acs$ModeTransport <-as.character(acs$ModeTransport)
acs$Occupation <-as.character(acs$Occupation)
acs$Income <-as.character(acs$Income)
``` 

+ Eighteen character variables and ten numerical variables



```{r}
# Remove unwanted variables: FlightNo, DepartureHr, DepartureMn
acs <- acs[ , -c(15:17, 27:28) ]
```


```{r}
# Missing values 
acs <- acs[!is.na(acs$Airline),]
acs <- acs[!is.na(acs$Age),]
acs <- acs[!is.na(acs$Gender),]
acs <- acs[!is.na(acs$Destination),]
# acs <- acs[!is.na(acs$Airfare),]
# acs <- acs[!is.na(acs$AccessCost),]
# acs <- acs[!is.na(acs$AccessTime),]
```



```{r}
summary(acs)

```



```{r}
airport <- acs %>% 
  group_by(Airport) %>% 
  summarise(count= n())
airline <- acs %>% 
  group_by(Airline) %>% 
  summarise(count= n())
age <- acs %>% 
  group_by(Age) %>% 
  summarise(count= n())
gender <- acs %>% 
  group_by(Gender) %>% 
  summarise(count= n())
nationality <- acs %>% 
  group_by(Nationality) %>% 
  summarise(count= n())
trippurpose <- acs %>% 
  group_by(TripPurpose) %>% 
  summarise(count= n())
provinceresidence <- acs %>% 
  group_by(ProvinceResidence) %>% 
  summarise(count= n())
grouptravel <- acs %>% 
  group_by(GroupTravel) %>% 
  summarise(count= n())
frequentdest <- acs %>% 
  group_by(FrequentFlightDestination) %>% 
  summarise(count= n())
destination <- acs %>% 
  group_by(Destination) %>% 
  summarise(count= n())
departuretime <- acs %>% 
  group_by(DepartureTime) %>% 
  summarise(count= n())
seatclass <- acs %>% 
  group_by(SeatClass) %>% 
  summarise(count= n())
modetrans <- acs %>% 
  group_by(ModeTransport) %>% 
  summarise(count= n())
occupation <- acs %>% 
  group_by(Occupation) %>% 
  summarise(count= n())
income <- acs %>% 
  group_by(Income) %>% 
  summarise(count= n())
```

```{r}
grid.arrange(
  airport %>% 
    ggplot(aes(x = Airport, y = count)) +
    geom_bar(stat = 'identity'),
  airline %>% 
    ggplot(aes(x = Airline, y = count)) +
    geom_bar(stat = 'identity'),
  age %>% 
    ggplot(aes(x = Age, y = count)) +
    geom_bar(stat = 'identity'),
  gender %>% 
    ggplot(aes(x = Gender, y = count)) +
    geom_bar(stat = 'identity'),
  nationality %>% 
    ggplot(aes(x = Nationality, y = count)) +
    geom_bar(stat = 'identity'),
  trippurpose %>% 
    ggplot(aes(x = TripPurpose, y = count)) +
    geom_bar(stat = 'identity'),
  provinceresidence %>% 
    ggplot(aes(x = ProvinceResidence, y = count)) +
    geom_bar(stat = 'identity'),
  grouptravel %>% 
    ggplot(aes(x = GroupTravel, y = count)) +
    geom_bar(stat = 'identity'),
  frequentdest %>% 
    ggplot(aes(x = FrequentFlightDestination, y = count)) +
    geom_bar(stat = 'identity'),
  destination %>% 
    ggplot(aes(x = Destination, y = count)) +
    geom_bar(stat = 'identity'),
  departuretime %>% 
    ggplot(aes(x = DepartureTime, y = count)) +
    geom_bar(stat = 'identity'),
  seatclass %>% 
    ggplot(aes(x = SeatClass, y = count)) +
    geom_bar(stat = 'identity'),
  modetrans %>% 
    ggplot(aes(x = ModeTransport, y = count)) +
    geom_bar(stat = 'identity'),
  occupation %>% 
    ggplot(aes(x = Occupation, y = count)) +
    geom_bar(stat = 'identity'),
  income %>% 
    ggplot(aes(x = Income, y = count)) +
    geom_bar(stat = 'identity'),
  ncol = 4

)
```


```{r}
grid.arrange(
  acs %>% 
    ggplot(aes(TripDuration)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(FlyingCompanion)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(NoTripsLastYear)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(Airfare)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(NoTransport)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(AccessCost)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(AccessTime)) +
    geom_histogram(),
  ncol = 2
)

```



```{r}
# Remove outliers, try out different restrictions
acs <- acs %>% filter(TripDuration <= 200,
                      FlyingCompanion <= 10,
                      NoTripsLastYear <= 20,
                      Airfare <= 150,
                      AccessCost <= 60000,
                      AccessTime <= 200)


```








