---
title: "BUAN_5310 Group_Project"
author: "Florence Yan, Haodi Tu, Huibo Jia, Qiyu Ye"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '3'
  html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r message = FALSE, echo = FALSE, error = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


# 1. Data Loading and Preperation
```{r message = FALSE, echo = FALSE, error = FALSE}
library(tidyverse)
library(GGally)
library(ggplot2)
library(readxl)
library(kableExtra)
library(gridExtra)
library(outliers)
library(Hmisc)
library(DMwR)
library(here)
```


```{r}
# Load data
## CSV file
acs <- read.csv('airport_choice_survey_modified.csv')
#traffic <- read.csv('traffic.csv')
#province <- read.csv('province.csv')
#price <- read.csv('price.csv')
## XLSX file
# acs <- read_excel("airport_choice_survey_EN_ver2.0_Capstone.xlsx", sheet = 'Data')
# traffic <- read_excel("Airport_Airline_data.xlsx", sheet = 1)
# province <- read_excel("Airport_Airline_data.xlsx", sheet = 3)
# price <- read_excel("Airport_Airline_data.xlsx", sheet = 2)
```


```{r}
# Rename columns in R
names(acs)[1]<-"ID"
# names(price)[1] <- "Airport"
# names(province)[1] <- "Airport"
# names(province)[4] <- "Travel.time.min"
# names(traffic)[1] <- "Airport"
```


```{r}
str(acs)
summary(acs)
```

+ Data type transfermation:
    + Seventeen character variables (ID excluded) and ten numerical variables
    
    + Numeric to factor: Airport, Airline, Gender, Nationality, TripPurpose, ProvinceResidence, GroupTravel, Destination, DepartureTime, SeatClass, ModeTransport, Occupation, Income
    
    + Remove unwanted variables
    + FlightNo: Don't match any other variables from data;
    + DepartureHr: Can use Departure time;
    + DepartureMn: Can use Departure tume; too many missing values;
    + MileageAireline: Too many missing values
    + Mileage: Too many missing values
    

```{r}
# Data cleaning
acs[2] <- ifelse(acs[2] == 1, 'ICN', 'GMP') 
  
acs[3] <- ifelse(acs[3] == 1, 'Korean',
           (ifelse(acs[3] == 2, 'Korean',
              (ifelse(acs[3] == 3, 'Korean', 'Foreign'))))
                   )
acs[4] <- ifelse(acs[4] <= 50 , '<=50', '>50')
acs[7] <- ifelse(acs[7] == 1, 'Leisure', 'Business')

# Remove ID column
acs <- select(acs, -1)

# Remove unwanted variables: FlightNo, FrequentFlightDestination, DepartureHr, DepartureMn, Mileage, MileageAireline
acs <- acs[ , -c(12, 14:16, 26,27) ]
```


```{r}
# Convert data type 
names <- c(1:6,9,10,12:14,17,20,21)
acs[,names] <- lapply(acs[,names] , factor)

# acs$Age <- as.factor(acs$Age)
# acs$Airport <- as.factor(acs$Airport)
# acs$Airline <- as.factor(acs$Airline)
# acs$Gender <- as.factor(acs$Gender)
# acs$Nationality <-as.factor(acs$Nationality)
# acs$TripPurpose <-as.factor(acs$TripPurpose)
# acs$ProvinceResidence <-as.factor(acs$ProvinceResidence)
# acs$GroupTravel <-as.factor(acs$GroupTravel)
# acs$Destination <-as.factor(acs$Destination)
# acs$DepartureTime <-as.factor(acs$DepartureTime)
# acs$SeatClass <-as.factor(acs$SeatClass)
# acs$ModeTransport <-as.factor(acs$ModeTransport)
# acs$Occupation <-as.factor(acs$Occupation)
# acs$Income <-as.factor(acs$Income)

summary(acs)
``` 

+ Missing values 
    + Airline(10); Age(1); Gender(3); Destination(4); SeatClass(4); Airfare(86); AccessCost(97); Income(132)
    + Remove missing values from age, gender, destination, seatclass;
    + Impute NA in airline(categorial), airfare(numerical), accessCost(numerical), income(categorial)


```{r}
# Missing Values

# Remove
acs <- acs[!is.na(acs$Age),]
acs <- acs[!is.na(acs$Gender),]
acs <- acs[!is.na(acs$Destination),]
acs <- acs[!is.na(acs$SeatClass),]

# Replace numerical variables' NAs with mean

acs$Airfare[is.na(acs$Airfare)] <- mean(acs$Airfare, na.rm = T)
acs$AccessCost[is.na(acs$AccessCost)] <- mean(acs$AccessCost, na.rm = T)

# impute(acs$Age, mean)
# impute(acs$TripDuration, mean)
# impute(acs$FlyingCompanion, mean)
# impute(acs$NoTripsLastYear, mean)
# impute(acs$Airfare, mean)
# impute(acs$NoTransport, mean)
# impute(acs$AccessCost, mean)
# impute(acs$AcessTime, mean)

# Replace categorical variables with KNN
acs_na <- knnImputation(acs)

# Check NA
anyNA(acs_na)

summary(acs_na)
```


```{r}
# Treat outliers
# reference: https://stackoverflow.com/questions/4787332/how-to-remove-outliers-from-a-dataset
# remove_outliers <- function(x, na.rm = TRUE, ...) {
#   qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
#   H <- 1.5 * IQR(x, na.rm = na.rm)
#   y <- x
#   y[x < (qnt[1] - H)] <- NA
#   y[x > (qnt[2] + H)] <- NA
#   y
# }
# y <- remove_outliers(acs$Age)
# par(mfrow = c(1, 2))
# boxplot(acs$Age)
# boxplot(y)
# y <- remove_outliers(acs$TripDuration)
# par(mfrow = c(1, 2))
# boxplot(acs$TripDuration)
# boxplot(y)
# y <- remove_outliers(acs$FlyingCompanion)
# par(mfrow = c(1, 2))
# boxplot(acs$FlyingCompanion)
# boxplot(y)
# y <- remove_outliers(acs$NoTripsLastYear)
# par(mfrow = c(1, 2))
# boxplot(acs$NoTripsLastYear)
# boxplot(y)
# y <- remove_outliers(acs$Airfare)
# par(mfrow = c(1, 2))
# boxplot(acs$Airfare)
# boxplot(y)
# y <- remove_outliers(acs$NoTransport)
# par(mfrow = c(1, 2))
# boxplot(acs$NoTransport)
# boxplot(y)
# y <- remove_outliers(acs$AccessCost)
# par(mfrow = c(1, 2))
# boxplot(acs$AccessCost)
# boxplot(y)
# y <- remove_outliers(acs$AccessTime)
# par(mfrow = c(1, 2))
# boxplot(acs$AccessTime)
# boxplot(y)

# summary(acs)
```


```{r}
# Outliers - numerical
outlier(acs_na$TripDuration)
outlier(acs_na$FlyingCompanion)
outlier(acs_na$NoTripsLastYear)
outlier(acs_na$Airfare)
outlier(acs_na$NoTransport)
outlier(acs_na$AccessCost)
outlier(acs_na$AccessTime)
# 
# Remove Outliers
acs_out <- acs_na %>%
  filter(TripDuration != 730,FlyingCompanion != 34, NoTripsLastYear != 122,Airfare != 260,NoTransport != 4, AccessCost != 350000, AccessTime != 390)
```


```{r}
summary(acs_out)
```


+ Observations on the data:
  + 469 observations after eliminating missing values (originally 488);
  + Airport: more choice on GMP (241-228);
  + Airline: Most are Korean Airlines (330-139);
  + Most are people under or equal to 50 years old;
  + Equivalent gender distribution (220-249);
  + The majorities are Koreans;
  + The mahorities travel for leisure;
  + Trip duration is highly positively skewed;
  + The number of flying companions is positively skewed; most groups are under 3 members;
  + The majorities are from Seoul;
  + The majorities are NOT travel in group;
  + The number of trips last year is positively skewed; most people traveled less than 3 times last year;
  + Most people fly to Southeast Asia and Japan (164-150-131);
  + Most people choose the departure time between 12pm - 6pm;
  + The majorities take economy class;
  + Airfare is positively skewed;
  + Most people take one transport to the airport;
  + The majorities take public transportations such as Airport Limousine and Subway;
  + Access cost is highly positively skewed; there are outliers on bothe sides;
  + Most people are business workers;
  + Most people's income are from 30 ~ 80 Million Won;
  
```{r}
str(acs_out)
```

  
  + Categorical: Airport, Airline, Age, Gender, Nationality, TripPurpose, ProvinceRsidence, GroupTravel, Destination, DepartureTime, SeatClass, ModeTransportation, Occupation, Income
  
  + Numerical: TripDuration, FlyingCompanion, NoTripLastYeaar, Airfare, NoTranport, AccessCost, AccessTime


```{r}
# Data Vis
## Categorical
airport <- acs_out %>% 
  group_by(Airport) %>% 
  summarise(count= n())
airline <- acs_out %>% 
  group_by(Airline) %>% 
  summarise(count= n())
age <- acs_out %>% 
  group_by(Age) %>% 
  summarise(count= n())
gender <- acs_out %>% 
  group_by(Gender) %>% 
  summarise(count= n())
nationality <- acs_out %>% 
  group_by(Nationality) %>% 
  summarise(count= n())
trippurpose <- acs_out %>% 
  group_by(TripPurpose) %>% 
  summarise(count= n())
provinceresidence <- acs_out %>% 
  group_by(ProvinceResidence) %>% 
  summarise(count= n())
grouptravel <- acs_out %>% 
  group_by(GroupTravel) %>% 
  summarise(count= n())
destination <- acs_out %>% 
  group_by(Destination) %>% 
  summarise(count= n())
departuretime <- acs_out %>% 
  group_by(DepartureTime) %>% 
  summarise(count= n())
seatclass <- acs_out %>% 
  group_by(SeatClass) %>% 
  summarise(count= n())
modetrans <- acs_out %>% 
  group_by(ModeTransport) %>% 
  summarise(count= n())
occupation <- acs_out %>% 
  group_by(Occupation) %>% 
  summarise(count= n())
income <- acs_out %>% 
  group_by(Income) %>% 
  summarise(count= n())
```


```{r}
grid.arrange(
  airport %>% 
    ggplot(aes(x = Airport, y = count)) +
    geom_bar(stat = 'identity'),
  age %>% 
    ggplot(aes(x = Age, y = count)) +
    geom_bar(stat = 'identity'),
  airline %>% 
    ggplot(aes(x = Airline, y = count)) +
    geom_bar(stat = 'identity'),
  gender %>% 
    ggplot(aes(x = Gender, y = count)) +
    geom_bar(stat = 'identity'),
  nationality %>% 
    ggplot(aes(x = Nationality, y = count)) +
    geom_bar(stat = 'identity'),
  trippurpose %>% 
    ggplot(aes(x = TripPurpose, y = count)) +
    geom_bar(stat = 'identity'),
  provinceresidence %>% 
    ggplot(aes(x = ProvinceResidence, y = count)) +
    geom_bar(stat = 'identity'),
  grouptravel %>% 
    ggplot(aes(x = GroupTravel, y = count)) +
    geom_bar(stat = 'identity'),
  destination %>% 
    ggplot(aes(x = Destination, y = count)) +
    geom_bar(stat = 'identity'),
  departuretime %>% 
    ggplot(aes(x = DepartureTime, y = count)) +
    geom_bar(stat = 'identity'),
  seatclass %>% 
    ggplot(aes(x = SeatClass, y = count)) +
    geom_bar(stat = 'identity'),
  modetrans %>% 
    ggplot(aes(x = ModeTransport, y = count)) +
    geom_bar(stat = 'identity'),
  occupation %>% 
    ggplot(aes(x = Occupation, y = count)) +
    geom_bar(stat = 'identity'),
  income %>% 
    ggplot(aes(x = Income, y = count)) +
    geom_bar(stat = 'identity'),
  ncol = 4
)
```



```{r}
# Categorical Variables - Airport
grid.arrange(
  acs_out %>% 
    ggplot(aes(Gender,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Age,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Nationality, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(TripPurpose, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ProvinceResidence, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(GroupTravel,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Destination, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(DepartureTime, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(SeatClass, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ModeTransport, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Occupation, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Income, fill = Airport)) +
    geom_bar(position = "dodge"),
  ncol = 3
)
```
+ Observations on the categorical variables (airport):
  + Variable Gender, Group Travel, SeatClass have similar pattern(counts) on both airports;
  + We can remove Gender, Group Travel, SeatClass from independent variables.

```{r}
# remove Gender, Group Travel, Seat Class
# Airport Model
acs_ap <- subset(acs_out, select = -c(Gender, GroupTravel, SeatClass))
```


```{r}
# Categorical Variables - Airline
grid.arrange(
  acs_out %>% 
    ggplot(aes(Gender,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Age,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Nationality, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(TripPurpose, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ProvinceResidence, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(GroupTravel,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Destination, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(DepartureTime, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(SeatClass, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ModeTransport, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Occupation, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Income, fill = Airline)) +
    geom_bar(position = "dodge"),
  ncol = 3
)
```

+ Observations on the categorical variables (airline):
  + All features are sensitive to the choice of airline; nothing need to be removed
  
```{r}
# Airline Model
acs_al <- acs_out
```


```{r}
# Numerical
grid.arrange(
  acs_out %>% 
    ggplot(aes(TripDuration)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(FlyingCompanion)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(NoTripsLastYear)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(Airfare)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(NoTransport)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(AccessCost)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(AccessTime)) +
    geom_histogram(),
  ncol = 2
)
```


```{r}
# Correlation plot
cor_plot <- acs_out %>%
  select(TripDuration, FlyingCompanion, NoTripsLastYear, NoTransport, Airfare, AccessCost, AccessTime)
cor_plot %>%
  ggpairs()
```



```{r}
# airline with all numerical variables
airline_num <- acs_al %>% 
  group_by(Airline) %>% 
  summarise(count = n(),
  mean_tripdu = mean(TripDuration),
  mean_flycom = mean(FlyingCompanion),
  mean_notrip = mean(NoTripsLastYear),
  mean_airfare = mean(Airfare),
  mean_noTrans = mean(NoTransport),
  mean_accessc = mean(AccessCost),
  mean_accesst = mean(AccessTime)
  ) %>% 
  arrange(desc(count))
airline_num
airline_num_table <- kable(airline_num) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
airline_num_table
```


```{r}
# airport with all numerical variables
airport_num <- acs_ap %>% 
  group_by(Airport) %>% 
  summarise(count = n(),
  mean_tripdu = mean(TripDuration),
  mean_flycom = mean(FlyingCompanion),
  mean_notrip = mean(NoTripsLastYear),
  mean_airfare = mean(Airfare),
  mean_noTrans = mean(NoTransport),
  mean_accessc = mean(AccessCost),
  mean_accesst = mean(AccessTime)
  ) %>% 
  arrange(desc(count))
airport_num
airport_num_table <- kable(airport_num) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
airport_num_table
```



```{r}
# Write CSV in R

## Airport Model
# write.csv(acs_ap, file = "acs_ap.csv")
# write.csv(acs_al, file = "acs_al.csv")
```