
---
title: "BUAN_5310 Group_Project"
author: "Florence Yan, Haodi Tu, Huibo Jia, Qiyu Ye"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '3'
  html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r message = FALSE, echo = FALSE, error = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


# 1. Data Loading and Preperation
```{r message = FALSE, echo = FALSE, error = FALSE}
library(tidyverse)
library(GGally)
library(ggplot2)
library(readxl)
library(kableExtra)
library(gridExtra)
library(outliers)
library(Hmisc)
library(here)
```


```{r}
# Load data
## CSV file
acs <- read.csv('airport_choice_survey_modified.csv')
#traffic <- read.csv('traffic.csv')
#province <- read.csv('province.csv')
#price <- read.csv('price.csv')
## XLSX file
# acs <- read_excel("airport_choice_survey_EN_ver2.0_Capstone.xlsx", sheet = 'Data')
# traffic <- read_excel("Airport_Airline_data.xlsx", sheet = 1)
# province <- read_excel("Airport_Airline_data.xlsx", sheet = 3)
# price <- read_excel("Airport_Airline_data.xlsx", sheet = 2)
```


```{r}
# Rename columns in R
names(acs)[1]<-"ID"
names(price)[1] <- "Airport"
names(province)[1] <- "Airport"
names(province)[4] <- "Travel.time.min"
names(traffic)[1] <- "Airport"
```


```{r}
str(acs)
summary(acs)
```

+ Data type transfermation:
    + Seventeen character variables (ID excluded) and ten numerical variables
    
    + Numeric to factor: Airport, Airline, Gender, Nationality, TripPurpose, ProvinceResidence, GroupTravel, Destination, DepartureTime, SeatClass, ModeTransport, Occupation, Income
    
+ Missing values 
    + Eliminate missing values from Airline, age, gender, destination, Airfare, AccessCost, AccessTime

+ Remove unwanted variables
    + FlightNo: Don't match any other variables from data;
    + DepartureHr: Departure time;
    + DepartureMn: Departure tume; too many missing values;
    + MileageAireline: Too many missing values
    + Mileage: Too many missing values
    
+ Observations on the data:
  + 170 observations after eliminating missing values (originally 488);
  + Airport: more choice on GMP (49-83);
  + Airline: KE the most, OZ the least (41-26);
  + Most are middle age people;
  + Equivalent gender distribution (70-62);
  + The majorities are Koreans;
  + The mahorities travel for leisure;
  + Trip duration is highly positively skewed;
  + The number of flying companions is positively skewed; most groups are under 3 members;
  + The majorities are from Seoul;
  + The majorities are NOT travel in group;
  + The number of trips last year is positively skewed; most people traveled less than 3 times last year;
  + Most people fly to Southeast Asia and Japan;
  + Most people choose the departure time between 12pm - 6pm;
  + The majorities take economy class;
  + Airfare is positively skewed; there are outliers on both sides;
  + Most people take 1 transport to the airport;
  + The majorities take public transportations such as Airport Limousine and Subway;
  + Access cost is highly positively skewed; there are outliers on bothe sides;
  + Most people are business workers;
  + Most people's income are from 30 ~ 80 Million Won;
  + The majorities are either KE memberships or none;
  
  + Categorical: Airport, Aireline, Gender, Nationality, TripPurpose, ProvinceRsidence, GroupTravel, Destination,     DepartureTime, SeatClass, ModeTransportation, Occupation, Income
  
  + Numerical: Age, TripDuration, FlyingCompanion, NoTripLastYeaar, Airfare, NoTranport, AccessCost, AccessTime
    

```{r}
# Remove ID column
acs <- select(acs, -1)

# Remove unwanted variables: FlightNo, FrequentFlightDestination, DepartureHr, DepartureMn, Mileage, MileageAireline
acs <- acs[ , -c(12, 14:16, 26,27) ]
```


```{r}
# Convert data type 
acs$Airport <- as.factor(acs$Airport)
acs$Airline <- as.factor(acs$Airline)
acs$Gender <- as.factor(acs$Gender)
acs$Nationality <-as.factor(acs$Nationality)
acs$TripPurpose <-as.factor(acs$TripPurpose)
acs$ProvinceResidence <-as.factor(acs$ProvinceResidence)
acs$GroupTravel <-as.factor(acs$GroupTravel)
acs$Destination <-as.factor(acs$Destination)
acs$DepartureTime <-as.factor(acs$DepartureTime)
acs$SeatClass <-as.factor(acs$SeatClass)
acs$ModeTransport <-as.factor(acs$ModeTransport)
acs$Occupation <-as.factor(acs$Occupation)
acs$Income <-as.factor(acs$Income)
``` 


```{r}
# Data Vis
## Categorical
airport <- acs %>% 
  group_by(Airport) %>% 
  summarise(count= n())
airline <- acs %>% 
  group_by(Airline) %>% 
  summarise(count= n())
age <- acs %>% 
  group_by(Age) %>% 
  summarise(count= n())
gender <- acs %>% 
  group_by(Gender) %>% 
  summarise(count= n())
nationality <- acs %>% 
  group_by(Nationality) %>% 
  summarise(count= n())
trippurpose <- acs %>% 
  group_by(TripPurpose) %>% 
  summarise(count= n())
provinceresidence <- acs %>% 
  group_by(ProvinceResidence) %>% 
  summarise(count= n())
grouptravel <- acs %>% 
  group_by(GroupTravel) %>% 
  summarise(count= n())
destination <- acs %>% 
  group_by(Destination) %>% 
  summarise(count= n())
departuretime <- acs %>% 
  group_by(DepartureTime) %>% 
  summarise(count= n())
seatclass <- acs %>% 
  group_by(SeatClass) %>% 
  summarise(count= n())
modetrans <- acs %>% 
  group_by(ModeTransport) %>% 
  summarise(count= n())
occupation <- acs %>% 
  group_by(Occupation) %>% 
  summarise(count= n())
income <- acs %>% 
  group_by(Income) %>% 
  summarise(count= n())
```


```{r}
grid.arrange(
  airport %>% 
    ggplot(aes(x = Airport, y = count)) +
    geom_bar(stat = 'identity'),
  airline %>% 
    ggplot(aes(x = Airline, y = count)) +
    geom_bar(stat = 'identity'),
  gender %>% 
    ggplot(aes(x = Gender, y = count)) +
    geom_bar(stat = 'identity'),
  nationality %>% 
    ggplot(aes(x = Nationality, y = count)) +
    geom_bar(stat = 'identity'),
  trippurpose %>% 
    ggplot(aes(x = TripPurpose, y = count)) +
    geom_bar(stat = 'identity'),
  provinceresidence %>% 
    ggplot(aes(x = ProvinceResidence, y = count)) +
    geom_bar(stat = 'identity'),
  grouptravel %>% 
    ggplot(aes(x = GroupTravel, y = count)) +
    geom_bar(stat = 'identity'),
  destination %>% 
    ggplot(aes(x = Destination, y = count)) +
    geom_bar(stat = 'identity'),
  departuretime %>% 
    ggplot(aes(x = DepartureTime, y = count)) +
    geom_bar(stat = 'identity'),
  seatclass %>% 
    ggplot(aes(x = SeatClass, y = count)) +
    geom_bar(stat = 'identity'),
  modetrans %>% 
    ggplot(aes(x = ModeTransport, y = count)) +
    geom_bar(stat = 'identity'),
  occupation %>% 
    ggplot(aes(x = Occupation, y = count)) +
    geom_bar(stat = 'identity'),
  income %>% 
    ggplot(aes(x = Income, y = count)) +
    geom_bar(stat = 'identity'),
  ncol = 4
)
```



```{r}
# Categorical Variables
grid.arrange(
  acs %>% 
    ggplot(aes(Gender,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(Nationality, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(TripPurpose, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(ProvinceResidence, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(GroupTravel,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>%  
    ggplot(aes(Destination, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(DepartureTime, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(SeatClass, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(ModeTransport, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>%  
    ggplot(aes(Occupation, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs %>% 
    ggplot(aes(Income, fill = Airport)) +
    geom_bar(position = "dodge"),
  ncol = 3
)
```
+ Observations on the categorical variables:
  + Variable Gender, Group Travel, SeatClass have similar pattern(counts) on both airports;
  + We can remove Gender, Group Travel, SeatClass from dependent variables.


```{r}
# remove Gender, Group Travel, Seat Class
acs <- subset(acs, select = -c(Gender, GroupTravel, SeatClass))
```

```{r}
# Numerical
grid.arrange(
  acs %>% 
    ggplot(aes(Age)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(TripDuration)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(FlyingCompanion)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(NoTripsLastYear)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(Airfare)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(NoTransport)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(AccessCost)) +
    geom_histogram(),
  acs %>% 
    ggplot(aes(AccessTime)) +
    geom_histogram(),
  ncol = 2
)
```


```{r}
# Correlation plot
cor_plot <- acs %>%
  select(Age, TripDuration, FlyingCompanion, NoTripsLastYear, NoTransport, Airfare, AccessCost, AccessTime)
cor_plot %>%
  ggpairs()
```



```{r}
# Outliers - numerical
outlier(acs$Age)
outlier(acs$TripDuration)
outlier(acs$FlyingCompanion)
outlier(acs$NoTripsLastYear)
outlier(acs$Airfare)
outlier(acs$NoTransport)
outlier(acs$AccessCost)
outlier(acs$AccessTime)

# Remove Outliers
acs <- acs %>% 
  filter(Age!=70, TripDuration!=730,FlyingCompanion!=34, NoTripsLastYear!=30,Airfare!=200,NoTransport!=3, AccessCost!=350000, AccessTime!=390)

```

```{r}
# Impute Missing Value

# Replace numerical variables' NAs with mean
impute(acs$Age, mean)
impute(acs$TripDuration, mean)
impute(acs$FlyingCompanion, mean)
impute(acs$NoTripsLastYear, mean)
impute(acs$Airfare, mean)
impute(acs$NoTransport, mean)
impute(acs$AccessCost, mean)
impute(acs$AcessTime, mean)

# Replace categorical variables' NAs with median
impute(acs$Nationality, median)
impute(acs$TripPurpose, median)
impute(acs$ProvinceResidence, median)
impute(acs$Destination, median)
impute(acs$DepartureTime, median)
impute(acs$ModeTransport, median)
impute(acs$Occupation, median)
impute(acs$Income, median)
```



```{r}
# airline with all numerical variables
airline_num <- acs %>% 
  group_by(Airline) %>% 
  summarise(count = n(),
  mean_age = mean(Age),
  mean_tripdu = mean(TripDuration),
  mean_flycom = mean(FlyingCompanion),
  mean_notrip = mean(NoTripsLastYear),
  mean_airfare = mean(Airfare),
  mean_noTrans = mean(NoTransport),
  mean_accessc = mean(AccessCost),
  mean_accesst = mean(AccessTime)
  ) %>% 
  arrange(desc(count))

airline_num

airline_num_table <- kable(airline_num) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

airline_num_table
```


```{r}
# airport with all numerical variables
airport_num <- acs %>% 
  group_by(Airport) %>% 
  summarise(count = n(),
  mean_age = mean(Age),
  mean_tripdu = mean(TripDuration),
  mean_flycom = mean(FlyingCompanion),
  mean_notrip = mean(NoTripsLastYear),
  mean_airfare = mean(Airfare),
  mean_noTrans = mean(NoTransport),
  mean_accessc = mean(AccessCost),
  mean_accesst = mean(AccessTime)
  ) %>% 
  arrange(desc(count))

airport_num

airport_num_table <- kable(airport_num) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

airport_num_table
```



```{r}
# Write CSV in R
# write.csv(acs, file = "acs.csv")
```








