---
title: "BUAN_5310 Group_Project"
author: "Florence Yan, Haodi Tu, Huibo Jia, Qiyu Ye"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: '3'
  html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r message = FALSE, echo = FALSE, error = FALSE}
# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 
# Clear environmet of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE)lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), detach, character.only = TRUE, unload = TRUE)
```


# 1. Data Loading and Preperation
```{r message = FALSE, echo = FALSE, error = FALSE}
library(tidyverse)
library(GGally)
library(ggplot2)
#library(readxl)
library(kableExtra)
library(gridExtra)
library(outliers)
library(Hmisc)
library(DMwR)
#library(here)
library(dplyr)
```


```{r}
# Load data
## CSV file
acs <- read.csv('airport_choice_survey_modified.csv')
```


```{r}
str(acs)
summary(acs)
```


+ Data type transfermation:
    + Seventeen character variables (ID excluded) and ten numerical variables
    
    + Numeric to factor: Airport, Airline, Gender, Nationality, TripPurpose, ProvinceResidence, GroupTravel, Destination, DepartureTime, SeatClass, ModeTransport, Occupation, Income
    
    + Remove unwanted variables (6)
    + FlightNo: Don't match any other variables from data;
    + DepartureHr: Can use Departure time;
    + DepartureMn: Can use Departure tume; too many missing values;
    + AcessCost: Too many missing values
    + MileageAireline: Too many missing values
    + Mileage: Too many missing values

# 2. Basic EDA
```{r}
# Remove unwanted variables: FlightNo, DepartureHr, DepartureMn, Mileage, MileageAireline
acs <- acs[ , -c(14:16,22,26,27) ]
```


```{r}
# Convert data type 
acs$Airport <- as.factor(acs$Airport)
acs$Airline <- as.factor(acs$Airline)
acs$Gender <- as.factor(acs$Gender)
acs$Nationality <-as.factor(acs$Nationality)
acs$TripPurpose <-as.factor(acs$TripPurpose)
acs$ProvinceResidence <-as.factor(acs$ProvinceResidence)
acs$GroupTravel <-as.factor(acs$GroupTravel)
acs$Destination <-as.factor(acs$Destination)
acs$FrequentFlightDestination <- as.factor(acs$FrequentFlightDestination)
acs$DepartureTime <-as.factor(acs$DepartureTime)
acs$SeatClass <-as.factor(acs$SeatClass)
acs$ModeTransport <-as.factor(acs$ModeTransport)
acs$Occupation <-as.factor(acs$Occupation)
acs$Income <-as.factor(acs$Income)


summary(acs)
```


+ Missing values 
    + Airline(10); Age(1); Gender(3); Destination(4); SeatClass(4); Airfare(86); Income(132)
    + Remove missing values from age, airline, gender, destination, seatclass;
    + Impute NA in airfare(numerical), regroup income(categorial)

# 3. Missing Value
```{r}
# Missing Values
# Remove
acs <- acs[!is.na(acs$Age),]
acs <- acs[!is.na(acs$Airline),]
acs <- acs[!is.na(acs$Gender),]
acs <- acs[!is.na(acs$Destination),]
acs <- acs[!is.na(acs$SeatClass),]
# Replace Airfare NAs with means by groups
acs_na <- acs %>% 
  group_by(Airport, Airline, Destination) %>% 
  mutate_each(funs(replace(., which(is.na(.)), mean(., na.rm=TRUE))), 
       starts_with('Airfare'))


#summary(acs_na$Airfare)


# Regroup NAs in categorical variables (Income Millon Won)
acs_na[21] <- ifelse(acs_na[21] == 1, '<=30',
                (ifelse(acs_na[21] == 2, '30~150',
                  (ifelse(acs_na[21] == 3, '30~150',
                       (ifelse(acs_na[21] == 4, '30~150',   
                               (ifelse(acs_na[21] == 5, '30~150',
                                       (ifelse(acs_na[21] == 'NA', 'NA','150~200>')))))))))))
acs_na$Income[is.na(acs_na$Income)] <- '00'
acs_na$Income <- acs_na$Income %>% as.factor()
acs_na$Income = factor(acs_na$Income,levels(acs_na$Income)[c(2,1,4,3)])

# Remove NA in Airfare
acs_na <- acs_na[!is.na(acs_na$Airfare),]
summary(acs_na)

## Check NA
# anyNA(acs_na)

```


# 4. Outlier
```{r}
# Outliers - numerical
outlier(acs_na$TripDuration)
outlier(acs_na$FlyingCompanion)
outlier(acs_na$NoTripsLastYear) 
outlier(acs_na$NoTransport)
outlier(acs_na$AccessTime)

# Remove Outliers
acs_out <- acs_na %>%
  filter(TripDuration != 730,FlyingCompanion != 34,NoTripsLastYear != 122,NoTransport != 4, AccessTime != 390)
```


```{r}
summary(acs_out)
```


+ Observations on the data:
  + 463 observations after eliminating missing values (originally 488);
  + Airport: more choice on GMP (239-224);
  + Airline: LLC listed as the least;
  + Most passengers are aroudn 40;
  + Equivalent gender distribution (219-244);
  + The majorities are Koreans;
  + The mahorities travel for leisure;
  + Trip duration is highly positively skewed; most are <= 5 days;
  + The number of flying companions is positively skewed; most groups are under 3 members;
  + The majorities are from Seoul;
  + The majorities are NOT travel in group;
  + The number of trips last year is positively skewed; most people traveled less than 3 times last year;
  + Most people fly to Southeast Asia and Japan (161-151-131);
  + Most people choose the departure time between 12pm - 6pm;
  + The majorities take economy class;
  + Airfare is positively skewed;
  + Most people take one transport to the airport;
  + The majorities take public transportations such as Airport Limousine and Subway;
  + Access cost is highly positively skewed; there are outliers on bothe sides;
  + Most people are business workers;
  + Most people's income are from 30 ~ 80 Million Won; 126 'NA'
  
+ Questions:
  + Regroup TrupPurpose?
  + Regroup SeatClass?
  + Regroup ModeTransport?
  + Regroup Occupation?
  
```{r}
str(acs_out)
```

  + Categorical: Airport, Airline, Gender, Nationality, TripPurpose, ProvinceRsidence, GroupTravel, FrequentDestination, Destination, DepartureTime, SeatClass, ModeTransportation, Occupation, Income
  
  + Numerical: Age, TripDuration, FlyingCompanion, NoTripLastYeaar, Airfare, NoTranport, AccessTime
  
# 5. Visualizations
```{r}
# Data Vis
## Categorical
airport <- acs_out %>% 
  group_by(Airport) %>% 
  summarise(count= n())
airline <- acs_out %>% 
  group_by(Airline) %>% 
  summarise(count= n())
gender <- acs_out %>% 
  group_by(Gender) %>% 
  summarise(count= n())
nationality <- acs_out %>% 
  group_by(Nationality) %>% 
  summarise(count= n())
trippurpose <- acs_out %>% 
  group_by(TripPurpose) %>% 
  summarise(count= n())
provinceresidence <- acs_out %>% 
  group_by(ProvinceResidence) %>% 
  summarise(count= n())
grouptravel <- acs_out %>% 
  group_by(GroupTravel) %>% 
  summarise(count= n())
freqdes <- acs_out %>% 
  group_by(FrequentFlightDestination) %>% 
  summarise(count= n())
destination <- acs_out %>% 
  group_by(Destination) %>% 
  summarise(count= n())
departuretime <- acs_out %>% 
  group_by(DepartureTime) %>% 
  summarise(count= n())
seatclass <- acs_out %>% 
  group_by(SeatClass) %>% 
  summarise(count= n())
modetrans <- acs_out %>% 
  group_by(ModeTransport) %>% 
  summarise(count= n())
occupation <- acs_out %>% 
  group_by(Occupation) %>% 
  summarise(count= n())
income <- acs_out %>% 
  group_by(Income) %>% 
  summarise(count= n())
```



```{r}
grid.arrange(
  airport %>% 
    ggplot(aes(x = Airport, y = count)) +
    geom_bar(stat = 'identity'),
  airline %>% 
    ggplot(aes(x = Airline, y = count)) +
    geom_bar(stat = 'identity'),
  gender %>% 
    ggplot(aes(x = Gender, y = count)) +
    geom_bar(stat = 'identity'),
  nationality %>% 
    ggplot(aes(x = Nationality, y = count)) +
    geom_bar(stat = 'identity'),
  trippurpose %>% 
    ggplot(aes(x = TripPurpose, y = count)) +
    geom_bar(stat = 'identity'),
  provinceresidence %>% 
    ggplot(aes(x = ProvinceResidence, y = count)) +
    geom_bar(stat = 'identity'),
  grouptravel %>% 
    ggplot(aes(x = GroupTravel, y = count)) +
    geom_bar(stat = 'identity'),
  freqdes %>% 
    ggplot(aes(x = FrequentFlightDestination, y = count)) +
    geom_bar(stat = 'identity'),
  destination %>% 
    ggplot(aes(x = Destination, y = count)) +
    geom_bar(stat = 'identity'),
  departuretime %>% 
    ggplot(aes(x = DepartureTime, y = count)) +
    geom_bar(stat = 'identity'),
  seatclass %>% 
    ggplot(aes(x = SeatClass, y = count)) +
    geom_bar(stat = 'identity'),
  modetrans %>% 
    ggplot(aes(x = ModeTransport, y = count)) +
    geom_bar(stat = 'identity'),
  occupation %>% 
    ggplot(aes(x = Occupation, y = count)) +
    geom_bar(stat = 'identity'),
  income %>% 
    ggplot(aes(x = Income, y = count)) +
    geom_bar(stat = 'identity'),
  ncol = 4
)
```



## 5.1 Categorical Variables with Airport
```{r}
# Categorical Variables - Airport
# Airports distrubution is equivalent
grid.arrange(
  acs_out %>% 
    ggplot(aes(Airline,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Gender,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Nationality, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(TripPurpose, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ProvinceResidence, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(GroupTravel,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(FrequentFlightDestination,fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Destination, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(DepartureTime, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(SeatClass, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ModeTransport, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Occupation, fill = Airport)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Income, fill = Airport)) +
    geom_bar(position = "dodge"),
  ncol = 3
)
```

+ Observations on the categorical variables (airport):
  + Variable Gender, Group Travel, SeatClass have similar pattern(counts) on both airports;
  + We can remove Gender, Group Travel, SeatClass from dependent variables;
  
  + Korean Airline and Asiana have the similiar pattern on the choice of airports; (Regroup??)
  + Regroup Nationality into Korean and Foreign;
  + Regroup 2,3,4 in TripPurpose as they share similar pattern;
  + Regroup destination which has similar patterns? (1-2;3-4)
  + Regroup Occupation with induviduals with/without income;

### 5.11 Regroup Variables after Visualization -- Airport Model
```{r}
# drop variables
# Airport Model
acs_ap <- subset(acs_out, select = -c(Gender, GroupTravel, SeatClass))
```


```{r}
# Regroup
acs_ap[2] <- ifelse(acs_ap[2] == 1, 'Korean',
                    ifelse(acs_ap[2] == 2, 'Korean',
                           ifelse(acs_ap[2] == 3, 'LCC', 'Foreign')))

acs_ap[4] <- ifelse(acs_ap[4] == 1, 'Korean', 'Foreign')

acs_ap[8] <- ifelse(acs_ap[8] == 1, 'City',
                    ifelse(acs_ap[8] == 2, 'City',
                           ifelse(acs_ap[8] == 3, 'City', 'Other')))

acs_ap[17] <- ifelse(acs_ap[17] == 1, 'w/income',
                     ifelse(acs_ap[17] == 2, 'w/income',
                            ifelse(acs_ap[17] == 3, 'w/income',
                                   ifelse(acs_ap[17] == 4, 'w/income',
                                          ifelse(acs_ap[17] == 5, 'w/income',
                                                 ifelse(acs_ap[17] == 6, 'w/income',
                                                       ifelse(acs_ap[17] == 7, 'w/income',
                                                              ifelse(acs_ap[17] == 12, 'Other', 'no income'))))))))

acs_ap[15] <- ifelse(acs_ap[15] == 1, 'Personal',
                     ifelse(acs_ap[15] == 2, 'Personal',
                            ifelse(acs_ap[15] == 9, 'Personal',
                                   ifelse(acs_ap[15] == 10, 'Air',
                                          ifelse(acs_ap[15] == 11, 'Other', 'Public')))))

acs_ap[11] <- ifelse(acs_ap[11] == 1, 'China',
                    ifelse(acs_ap[11] == 2, 'Japan', 'Other'))

acs_ap[5] <- ifelse(acs_ap[5] == 1, 'Leisure','Other')

acs_ap[10] <- ifelse(acs_ap[10] == 1, 'SA', 
                     ifelse(acs_ap[10] == 2, 'China',
                            ifelse(acs_ap[10] == 3, 'Japan', 'Others')))
```


## 5.2 Categorical Variables with Airline
```{r}
# Categorical Variables - Airline
grid.arrange(
  acs_out %>% 
    ggplot(aes(Airport,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Gender,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Nationality, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(TripPurpose, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ProvinceResidence, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(GroupTravel,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(FrequentFlightDestination,fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Destination, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(DepartureTime, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(SeatClass, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(ModeTransport, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>%  
    ggplot(aes(Occupation, fill = Airline)) +
    geom_bar(position = "dodge"),
  acs_out %>% 
    ggplot(aes(Income, fill = Airline)) +
    geom_bar(position = "dodge"),
  ncol = 3
)
```

+ Observation from the data:
  + Remove GroupTravel;
  
  + Regroup SeatClass;
  + Regroup TripPurpose;
  + Regroup Nationality;

### 5.21 Regroup Variables after Visualization -- Airline Model
```{r}
# drop variables
# Airport Model
acs_al <- subset(acs_out, select = -c(GroupTravel))
```


```{r}
# Regroup
acs_al[5] <- ifelse(acs_al[5] == 1, 'Korean', 'Foreign')

acs_al[6] <- ifelse(acs_al[6] == 1, 'Leisure','Other')

acs_al[9] <- ifelse(acs_al[9] == 1, 'City', 
                     ifelse(acs_al[9] == 2, 'City',
                            ifelse(acs_al[9] == 3, 'City', 'Others')))

acs_al[11] <- ifelse(acs_al[11] == 1, 'SA', 
                     ifelse(acs_al[11] == 2, 'China',
                            ifelse(acs_al[11] == 3, 'Japan', 'Others')))

acs_al[17] <- ifelse(acs_al[17] == 1, 'Personal',
                     ifelse(acs_al[17] == 2, 'Personal',
                            ifelse(acs_al[17] == 9, 'Personal',
                                   ifelse(acs_al[17] == 10, 'Air',
                                          ifelse(acs_al[17] == 11, 'Other', 'Public')))))

acs_al[14] <- ifelse(acs_al[14] == 1, 'Economic','Other')

```



## 5.3 Numerical Variable
```{r}
# Numerical
grid.arrange(
  acs_out %>% 
    ggplot(aes(TripDuration)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(Age)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(FlyingCompanion)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(NoTripsLastYear)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(Airfare)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(NoTransport)) +
    geom_histogram(),
  acs_out %>% 
    ggplot(aes(AccessTime)) +
    geom_histogram(),
  ncol = 2
)
```
  

## 5.31 Correlation Between Numerical Variables
```{r}
# Correlation plot
cor_plot <- subset(acs_out, select = c(TripDuration, FlyingCompanion, NoTripsLastYear, NoTransport, Airfare, AccessTime))
cor_plot %>%
  ggpairs()
```
  
  
+ Observations on the data:
  + No Multicollinarity;
  
# 6. Logistic Modelling
## 6.1 Airport 
### 6.11 Train - Test (70/30)
```{r}
# Reference Category
acs_ap[1] <- ifelse(acs_ap[1] == 1, 'ICN','GMP')
acs_ap$Airport <- as.factor(acs_ap$Airport)
contrasts(acs_ap$Airport) # ICN = 1, GMP = 0

# Sampling 70/30
library(caret) 
set.seed(666) 
trainrows<-createDataPartition(acs_ap$Airport, p = 0.7, list=FALSE) 
train_set_ap<-acs_ap[trainrows,] 
test_set_ap<-acs_ap[-trainrows,]

# write.csv(train_set_ap, file = "train_airport.csv")
# write.csv(test_set_ap, file = "test_airport.csv")
```


```{r}
# Logistic 1
# first model -- before ANOVA
ap_logit_1 <- glm(Airport ~., data = train_set_ap, family=binomial("logit"))
print(ap_logit_1)
summary(ap_logit_1)
```


### 6.12 Anova Analysis
```{r}
anova(ap_logit_1, test="Chisq")
```

```{r}
#install.packages("car")
library(car)
vif(ap_logit_1)
```


```{r}
#Remove variables after Anova Analysis
train_set_ap2 <- subset(train_set_ap, select = -c(TripDuration, Destination, Airfare, FlyingCompanion, TripPurpose, ModeTransport))
```


### 6.13 Stepwide Model
```{r}
null = glm(Airport ~ 1, data = train_set_ap2, family=binomial("logit"))
full = glm(Airport ~., data = train_set_ap2, family=binomial("logit"))
step(null, scope = list(lower=null,upper=full),
     direction="both", criterion = "BIC")
```


```{r}
# Airport Model
ap_logit_2 <- glm(Airport ~., data = train_set_ap2, family=binomial("logit"))
summary(ap_logit_2)
```


```{r}
vif(ap_logit_2)
```


### 6.14 Confusion Matrix

```{r}
# Prediction - Training
#test_set_ap2 <- subset(test_set_ap, select = -c(TripDuration, Airfare, FlyingCompanion, AccessTime))
predicted <- plogis(predict(ap_logit_2, train_set_ap))
pred <- ifelse(predicted > 0.5, "ICN", "GMP")
pred <- as.factor(pred)
confusionMatrix(train_set_ap$Airport, pred)
```



```{r}
# Prediction - Testing
#test_set_ap2 <- subset(test_set_ap, select = -c(TripDuration, Airfare, FlyingCompanion, AccessTime))
predicted <- plogis(predict(ap_logit_2, test_set_ap))
pred <- ifelse(predicted > 0.5, "ICN", "GMP")
pred <- as.factor(pred)
confusionMatrix(test_set_ap$Airport, pred)
```

### 6.15 R-Square
```{r}
library(pscl)
pR2(ap_logit_2)
```

### 6.16 K-fold Cross Validation
```{r}
train_control <- trainControl(method='cv', number = 4)
model <- train(Airport ~., data = train_set_ap2, trControl = train_control, method="glm", family="binomial")
pred_k <- predict(model, newdata=test_set_ap)
confusionMatrix(data=pred_k, test_set_ap$Airport)
```


## 6.2 Airline
### 6.21 Train - Test (70/30)
```{r}
acs_al$Airline <- relevel(acs_al$Airline, ref=1)

# Sampling 70/30
library(caret) 
set.seed(666) 

trainrows_al<-createDataPartition(acs_al$Airline, p = 0.7, list=FALSE) 
train_set_al<-acs_al[trainrows_al,] 
test_set_al<-acs_al[-trainrows_al,]

# write.csv(train_set_al, file = "train_airline.csv")
# write.csv(test_set_al, file = "test_airline.csv")
```


### 6.22 Original Model - Airline
```{r}
# Multinomial Logistic 1
# first model -- before ANOVA
#install.packages('nnet')
library(nnet)

al_logit_1 <- multinom(Airline ~., data = train_set_al)
print(al_logit_1)
summary(al_logit_1)
```


### 6.23 Original Model - Coefficients
```{r}
summary(al_logit_1)$coefficients
```

### 6.24 Original Model - SE
```{r}
summary(al_logit_1)$standard.errors
```

### 6.25 Original Model - P Value
```{r}
zvalues <- summary(al_logit_1)$coefficients / summary(al_logit_1)$standard.errors

pnorm(abs(zvalues), lower.tail=FALSE)*2
```


### 6.26 Original Model Prediction

```{r}
# Prediction - Training
predicted_al <- predict (al_logit_1, train_set_al, "probs")

pred_al <- predict(al_logit_1, train_set_al)

confusionMatrix(train_set_al$Airline, pred_al)
```


```{r}
# Prediction - Testing 
predicted_al <- predict (al_logit_1, test_set_al, "probs")

pred_al <- predict(al_logit_1, test_set_al)

confusionMatrix(test_set_al$Airline, pred_al)
```


### 6.27 Original Model R-Square
```{r}
library(pscl)
pR2(al_logit_1)
```

### 6.28 Original Model K-fold Cross Validation
```{r}
train_control <- trainControl(method='cv', number = 4)
model_al <- train(Airline ~., data = train_set_al, trControl = train_control, method="multinom")
pred_k_al <- predict(model_al, newdata=test_set_al)
confusionMatrix(data=pred_k_al, test_set_al$Airline)
```

### 6.29 Original Model Stepwise
```{r}
null_al = multinom(Airline ~ 1, data = train_set_al)
full_al = multinom(Airline ~., data = train_set_al)
step(null_al, scope = list(lower=null_al,upper=full_al),
     direction="both", criterion = "BIC")
```


## 6.3 Airline Modified Model
```{r}
al_logit_2 <- multinom(Airline ~ Airfare * Destination + SeatClass + Nationality + Age + Gender + TripPurpose + Income + 
    Airport + DepartureTime + FrequentFlightDestination +
    TripDuration + NoTripsLastYear + FlyingCompanion, data = train_set_al)
print(al_logit_2)
summary(al_logit_2)
```


```{r}
summary(al_logit_2)$coefficients
```


```{r}
summary(al_logit_2)$standard.errors
```


```{r}
zvalues <- summary(al_logit_2)$coefficients / summary(al_logit_2)$standard.errors

pnorm(abs(zvalues), lower.tail=FALSE)*2
```


### 6.31 Confusion Matrix
```{r}
# Prediction
predicted_al <- predict (al_logit_2, test_set_al, "probs")

pred_al <- predict(al_logit_2, test_set_al)

confusionMatrix(test_set_al$Airline, pred_al)
```


### 6.31 R Squared
```{r}
library(pscl)
pR2(al_logit_2)
```

### 6.32 K-folders cross validation for Airline
```{r}
train_control <- trainControl(method='cv', number = 4)
model_al <- train(Airline ~ Destination + Airfare + ProvinceResidence + 
    Airport + NoTransport + FrequentFlightDestination + DepartureTime + 
    TripDuration + NoTripsLastYear + FlyingCompanion, data = train_set_al, trControl = train_control, method="multinom")
pred_k_al <- predict(model_al, newdata=test_set_al)
confusionMatrix(data=pred_k_al, test_set_al$Airline)
```







